Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-27 paper/high-assurance-contracts.tex
Light proofreading

Code contracts for the filter and monitor are shown in
\figref{fig:filter} and \figref{fig:monitor}.
The filter is direct: it defines the policy according to the well-formed requirement for data.
We now discuss in some detail the monitor.

@@

The policy definition only works if there is never more than one
outstanding request at a time; otherwise, the latency counter resets
incorrectly.  That requirement is encoded in the assumption on
\lineref{line:mon-assume} and is the same assumption used for the
system input.  The policy can be written without needing the
assumption, but it is much simpler to write with the assumption.

As shown in \figref{fig:hardened-certificate}, the cyber-hardened
system passes AGREE verification.  That means that the high-assurance
components protect the WM from the untrusted AI generating malformed
data, spontaneous responses, or delayed responses.  Synthesis must
generate precise implementations of the high-assurance component
specifications for the AGREE verification result to apply to the
deployed system.  Precise in this context means that the
implementations match the input to output relations defined in the
specifications.

>>>>

Code contracts for the filter and monitor are shown in
\figref{fig:filter} and \figref{fig:monitor}.
The filter is direct: it defines the policy according to the well-formed requirement for data.
We now discuss the monitor in some detail.

@@

The policy definition only works if there is never more than one
outstanding request at a time; otherwise, the latency counter resets
incorrectly.  That requirement is encoded in the assumption on
\lineref{line:mon-assume} and is the same assumption used for the
system input.  The policy can be written without the assumption, 
but the policy is much simpler to write with the assumption.

As shown in \figref{fig:hardened-certificate}, the cyber-hardened
system passes AGREE verification.  That means that the high-assurance
components protect the WM from the untrusted AI generating malformed
data, spontaneous responses, or delayed responses.  Synthesis must
generate precise implementations of the high-assurance component
specifications for the AGREE verification result to apply to the
deployed system.  Precise in this context means that the
implementations match the input-to-output relations defined in the
specifications.
